---
title: "CAPM_msft_spy"
author: "Sriraj Muddu"
date: "2025-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(ggplot2)
library(dplyr)
```

### Reading file data and plotting the relationship between return rates:

```{r}
totalReturn <- read_csv('totalReturnRates.csv')
totalReturn <- totalReturn %>%
  mutate(
    Excess_MSFT = `Return MSFT` - `Return T-Bill`,
    Excess_SPY = `Return S&P` - `Return T-Bill`
  )

ggplot(totalReturn, aes(x=Excess_MSFT, y = Excess_SPY)) + geom_point()

```

### Because the plot is visibly linear and there are not many outliers, we will attempt a simple linear regression

```{r}
regressionModel <- lm(Excess_MSFT  ~ Excess_SPY, data=totalReturn)

summary(regressionModel)

plot(regressionModel)
```



### Analysis:
*   In the Residuals vs. Fitted graph, the residuals cluster around 0, showing that a linear model was a good fit for this data. 
*   The Q-Q plot is relatively linear, showing that the probability distributions for Excess SPY and Excess MSFT are quite similar
*   The scale-location graph is roughly horizontal, suggesting a high degree of homoscedasticity
*   There are not an extreme quantity of outliers with high leverage, however there are a few

Sample Predictions:



```{r}

beta <- regressionModel$coefficients[2]

intercept <- regressionModel$coefficients[1]

estimatedMSFTReturn <- intercept + beta*(0.0022 - (4.31/31)) + (4.31/31) 

print(estimatedMSFTReturn)

```

### Although this estimation was not extremely accurate (the true daily return on this day was -0.0059%), by averaging the output over longer time frames the predictions become more accurate. 